Stack Safety as a Security Property

### 2020-09-08 rebuttal.txt

On the other hand, Skorstengaard relies on different prior intuitions:
for readers familiar with the behavior of pure stacks (or rather the
built-in oLCM stack), their property is more intuitive. For readers
versed in security, we believe there is value in a different
perspective.

(2) useful for reasoning: In order to reason about actual programs we
would indeed need to incorporate a "Meaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al] in mind.

(3) reusable in compiler chains: As you point out, this is not really
applicable, since this is a criterion tailored to what Skorstengaard
is aiming to do. We might consider what the equivalently tailored
criterion would be for us -- usable in "dynamic enforcement
environments" with potentially unsafe commodity compilers.

LEO: I'm REALLY not sure about this:
APT: Reviewer C interprets (4) to mean: 
"This criterion asks for an argument that any property of a program
that relies on stack safety can be proven with the characterization of stack safety."
Since we're in the business of _defining_ stack safety, this seems pretty circular to me!
Maybe the point is that we should not omit any characteristic of
everyone's informal notion of stack safety (for the set of language features
we support -- which is the business of (5)).  Can we claim that (informally, of course)?
(4) complete: Subject to the limitations of the formalization, our
properties should apply to any reasonable program.

@@

> ---------------------------------
> * You seem to say/suggest that the approach of Skorstengaard 2019b to defining stack safety is specific to capability machines.
>   Do you really think so and if so, why do you think their approach could not be applied to a different enforcement mechanism?
APT:  Sk2019b _define_ stack safety via a capability machine semantics that is supposed to embody stack
safety "by construction," and relating it to a standard semantics for the same machine via a full abstraction result.
We did not mean to imply that the same idea could not work for other machine models or enforcement mechanisms (although
this generalization is not actually in Sk2019b, even as suggested future work). Rather, we wished to distinguish our
approach from theirs by emphasizing that we define stack safety based not on any "correct by construction" 
machine tied to some flavor of enforcement,  but rather on more abstract notions of observable behavior. 

### 2020-09-09 rebuttal.txt

We thank the reviewers and in particular reviewer C for their
thoughtful comments.

We first discuss the most important points raised in reviews. Then, in
an optional appendix, we respond point-by-point to each individual
piece of reviewer feedback.

Reviewer C is particularly concerned with the way this work is
motivated. Our original goal in this work wasn't to formalize a stack
safety notion that is specific to micropolicies, but in hindsight we
agree that the result appears to be tailored to that particular
enforcement mechanism---in large part because of our presentation
choices and exposition-helping simplifications. In particular, we
believe that the enforcement model can be used (with some effort) to
describe capability-based enforcement mechanisms (as we state in
Section 2).  However, given that this effort didn't make it into the
final product, we agree that the material present would be more
accurately described as an abstract property capturing micropolicy
enforcement rather than the all-encompassing stack safety notion we
set out to state, and intend to do so for a final version.

BCP: Basically good, but I think we can be a little less apologetic, and
stronger on what we'd propose to do to fix it.

@@

All reviewers also wanted additional discussion of related work.  We
agree that there should be a clearer comparison to both Skorstengaard
papers, using the informal criteria layed out there. We plan to
include a discussion like the following:

(1) On intuition: The LSE part of property we present aims to
characterize stack safety in security terms. For readers familiar with
integrity/confidentiality/noninterference, the eager version should be
fairly intuitive. The lazy/observable properties, are less intuitive,
but more interesting in the violations they permit. The WBCF part simply
formalizes standard behavior of stack-based control flow.

By contrast, Skorstengaard relies on different prior intuitions:
for readers familiar with the behavior of pure stacks (or rather the
built-in oLCM stack), their property is more intuitive. For readers
versed in security, we believe there is value in a different
perspective.

@@

> ---------------------------------
> * You seem to say/suggest that the approach of Skorstengaard 2019b to defining stack safety is specific to capability machines.
>   Do you really think so and if so, why do you think their approach could not be applied to a different enforcement mechanism?

APT:  Sk2019b _define_ stack safety via a capability machine semantics that is supposed to embody stack
safety "by construction," and relating it to a standard semantics for the same machine via a full abstraction result.
We did not mean to imply that the same idea could not work for other machine models or enforcement mechanisms (although
this generalization is not actually in Sk2019b, even as suggested future work). Rather, we wished to distinguish our
approach from theirs by emphasizing that we define stack safety based not on any "correct by construction" 
machine tied to some flavor of enforcement,  but rather on more abstract notions of observable behavior.

BCP: Nice.

> * What exactly is the benefit of your approach to defining stack safety w.r.t. the approach of Skorstengaard 2019b?
>   Do you think it can be applied to more or less languages?
>   Do you think it is better suited or less well suited for reasoning about programs which depend on stack safety?
>   Do you think it is etc.
>
> * Do you think you could show safety of a specific example program that depends on stack safety (like the awkward example) and if so, how would such a proof work?
>
> * Do you think your approach to defining stack safety could be extended to languages with the following features (and if so, how?):
>   - varargs?  (seems problematic for call map)
>   - dynamic code generation (seems problematic for the function map, call map and return map)
>   - dynamic linking (seems problematic for the function map, call map and return map)
>   - self-editing code (seems problematic for call map and return map)
>   - tail calls (seems potentially okay, but I'd like to be sure)
>   - exceptions and stack unwinding
>   - closures (seems potentially problematic for precision of the entry map)
>   How would you extend your approach to define stack safety in the presence of these features?
>
> * Do you think your approach implies the following properties?
>   - temporal safety in the presence of closures (i.e. closures should only be invokable by the adversary after the adversary first receives a reference to them)
>   - encapsulation of closures: it should not be possible for the adversary to invoke a closure with a different environment than the one they received?
>   If not, do you think it should imply these properties and if so, how do you think it could be extended?
>
> * Are the lazy and strong variant of your properties specifically intended for the corresponding micropolicy-based enforcement techniques or do you believe they are more broadly applicable?

### 2020-09-09 rebuttal.txt

We thank the reviewers and in particular reviewer C for their thoughtful
comments.  We first discuss the most important points raised in
reviews. Then, in an optional appendix, we respond point-by-point to each
individual piece of reviewer feedback.

MOTIVATION

Reviewer C is particularly concerned with the way this work is
motivated. Our original goal in this work wasn't to formalize a stack safety
notion that is specific to micropolicies, but in hindsight we agree that the
result may appear to be tailored to that particular enforcement mechanism,
though we believe this is more a matter of presentation choices and
exposition-helping simplifications than a fundamental limitation. In
particular, we believe that the enforcement model can be used (with some
effort) to describe capability-based enforcement mechanisms, as we state in
Section 2.  However, given that this effort didn't make it into the final
product, we agree that the paper as it stands would be more accurately
described as an abstract property capturing micropolicy enforcement rather
than the all-encompassing stack safety notion we set out to state, and
intend to do so for a final version.

BCP: I.e., we plan to limit our claims rather than fixing the exposition?
Why not promise the latter (and lay out what we would do)?

RELATED WORK

All reviewers also wanted additional discussion of related work.  We agree
that there should be a clearer comparison to both Skorstengaard papers,
using the informal criteria proposed there. We plan to include a discussion
like the following:

(1) On intuition: The LSE part of the property we present aims to
characterize stack safety in security terms. For readers familiar with
integrity/confidentiality/noninterference, the eager version should be
fairly intuitive. The lazy/observable properties, are less intuitive,
but more interesting in the violations they permit. The WBCF part simply
formalizes standard behavior of stack-based control flow.

BCP: "more interesting in the violations they permit"???

@@

(3) reusable in compiler chains: As you point out, this is not really
applicable, since this is a criterion tailored to what Skorstengaard
is aiming to do. We might consider what the equivalently tailored
criterion would be for us -- usable in "dynamic enforcement
environments" with potentially unsafe commodity compilers.

LEO: I'm REALLY not sure about this:
APT: Reviewer C interprets (4) to mean:
"This criterion asks for an argument that any property of a program
that relies on stack safety can be proven with the characterization of stack safety."
Since we're in the business of _defining_ stack safety, this seems pretty circular to me!
Maybe the point is that we should not omit any characteristic of
everyone's informal notion of stack safety (for the set of language features
we support -- which is the business of (5)).  Can we claim that (informally, of course)?
(4) complete: Subject to the limitations of the formalization, our
properties should apply to any reasonable program.

(5) scalable: Dynamic code would pose a significant challenge in this
setup. In the tag world, we could handle generated code by tagging the
instructions that generate it, which would correspond to a map that
allows some instructions to update the maps, including potentially
itself.  On the other hand, we described how we would handle
coroutines, and threads would be similar. Basically when we lose the
monotonicity of contours throughout an execution trace, and we would
need to change the LSE property to vary at each context entry and and
to exit at each return.

ATTACKER MODEL

Finally, reviewer C is also concerned with the attacker model. The attacker
model we consider is discussed in Section 2.  In particular, lines 104-106
state that "the attacker can run arbitrary machine code" and that "hardware
and timing attacks are out of scope". The attacker model of the micropolicy
enforcement mechanism is described in [Roessler and Dehon 18].

BCP: Can we sketch it here?

@@

>   [Roessler and DeHon 2018]'s "lazy tagging and clearing" is itself not stack-safe according to this paper.
>   To understand the mechanism, this paper additionally defines the "observable" versions of stack safety.
>   But then why you didn't use the observable version as the authoritative definition?

BCP: This is a silly objection, but it should be addressed clearly and
strongly.  E.g.:

We propose two definitions of stack safety: one that is easier to understand
because it corresponds to a more naive view of what stack safety intuitively
means, and a slightly more complex and permissive one that (as Roessler and
Dehon showed) can be implemented more efficiently.  We believe both are of
interest.

> - This paper is lacking proper discussion on related work.
>
>    On the contrary to this paper's observation (L25), there're a few formalizations of stack safety (and rely/guarantee conditions for function invocation).
>       For example, see CompCert's assumption on function calls: https://github.com/AbsInt/CompCert/blob/94558ecb3e48261f12c644045d40c7d0784415e0/common/Events.v#L619

BCP: Obviously, this has to be addressed strongly and concretely.

### 2020-09-09 rebuttal.txt

Motivation - Applicability:

Our original goal in this work wasn't to formalize a stack safety
notion that is specific to micropolicies, but in hindsight we agree
that the result appears to be tailored to that particular enforcement
mechanism---in large part because of our presentation choices and
exposition-helping simplifications. In particular, we believe that the
enforcement model can be used (with some effort) to describe
capability-based enforcement mechanisms (as we state in Section 2).
However, given that this effort didn't make it into the final product,
we agree that the material present would be more accurately described
as an abstract property capturing micropolicy enforcement rather than
the all-encompassing stack safety notion we set out to state.
LEO: ...and we plan to do so for the full version?

Attacker Model:

The attacker model for the properties is discussed in the paper
(Section 2). For example, lines 104-106 state that "the attacker can
run arbitrary machine code" and that "hardware and timing attacks are
out of scope". The attacker model of the micropolicy enforcement
mechanism is described in [Roessler and Dehon 18].

5 Criteria - StkTokens:
LEO: Not really sure what to say here. 
(1) intuitive: this is subjective but we were aiming for a more extensional property than full abstraction from a "clearly stack safe" machine
(2) useful for reasoning: LEO: do we have anything to say here other than you're right?
(3) reusable in compiler chains: not really applicable?
(4) complete: ??
(5) scalable: what can we extend this to? the maps appear particularly restrictive here...

SNA: Thoughts on the criteria.
(1) The LSE property can be conceptually divided into the contour function, which divides the stack into
    HC/LC and HI/LI components, and the actual definitions of confidentiality and integrity w.r.t. that
    division. Insofar as confidentiality and integrity are believable, I believe the contour is very
    intuitive. Confidentiality is not especially intuitive, but is based on non-interference which
    is well-known. Eager integrity is pretty intuitive. The lazy properties are highly non-intuitive,
    which makes sense as the policies they aim to characterize permit violations of the standard intuition.

    The WBCF property simply describes the standard behavior of stack-based control flow, it seems very intuitive.

    Relating to Skorstengaard, they rely on different prior intuitions. Skorstengaard is intuitive to exactly the
    degree that one understands the behavior of a pure stack in general and the built-in stack of oLCM in
    particular. As the behavior of stacks is generally understood, Skorstengaard has an edge, but there is
    value in offering an intuition that is less circularly dependent on understanding stacks.
(2) We probably don't have anything to say here. A "Meaning of Memory Safety"-style frame rule would be just the
    ticket, but we haven't done it.
(3) Not really applicable, since this is a criterion tailored to what Skorstengaard is aiming to do. We might consider
    what the equivalently tailored criterion would be for us -- usable in "dynamic enforcement environments" with
    potentially unsafe commodity compilers? Where we score well but not perfectly, because while we do need some compiler 
    support it's in the form of very basic control flow information.
(4) Subject to the limitations of the formalization, our properties should apply to any reasonable program.
    But we would need to make some argument that we're not missing something obvious.
(5) It would be very challenging to mess with dynamic code, unfortunately. In the tag world we would handle
    generated code by tagging the instructions that generate it, I suppose. Which would correspond to
    a map that allows some instructions to update the maps, including potentially itself, etc...

    On the other hand, we described how we would handle coroutines, and threads would be similar. Basically
    when we lose the property of the contour that exiting a context means either shrinking access monotonically
    or never returning to that context, we need to change the LSE property to vary at each entry to a context
    and test at each exit from it. But once that is done the space of threads and coroutines should be wide open.
    As for WBCF, we would need to update Control Separation and Entry Integrity to account for changes in
    acceptable modes of control transfer. Return integrity applies to calls and returns even if separated by
    yields.

SNA: Thoughts on closures (very sketchy).

  Suppose we added yet another partial map (sigh) representing the sealing of a closure. Suppose as well that our
  model is enhanced to track the provenance of values as discussed in the future work section on stack-derived
  pointers. A closure map would take a code address as usual and yield: a register r that holds the pointer, an
  entry point e, a unique Seal identifier i, and a set of components ks. We extend the tuple of a security state a
  contour can give with (forall i, Seal i). When we take a step from an instruction where the closure map is defined,
  we update the contour C so that for each k in ks, C(k) is (*,*,Seal i). We also need to add state to track the
  association between i, e, and r, and carry that association to any k with pointer provenance from r.
  Finally, we modify call maps to give an optional component whose contents are being used as a function pointer.

  Then, when a call map says that we are making a call using a closure associated with (Seal i), the contour
  update sets all (Seal i) components (LC,LI) and LSE works just the same, treating sealed components as (HC/HI).
  WBCF will need an extra clause stating that we really did jump to e. (I'm a little unclear as to whether a
  closure should be re-sealed on return, but we can do that if we need to.)

  (Notes: arg, maybe we actually need a list of closures.)

  To answer the questions: yes, we believe this can be extended to closures, and with these additions stack safety
  would indeed imply both temporal safety and encapsulation of closures.

### 2020-09-09 rebuttal.txt

(2) useful for reasoning: In order to reason about actual programs we
would indeed need to incorporate a "Meaning of Memory Safety"-style
frame rule. Our goal with this paper was to distill the essence of
stack safety without adding the complex (but solved) overhead of
dealing with heap locations. But the properties (and the testing
framework behind it) were designed with [Azevedo et al] in mind.

(3) reusable in compiler chains: As you point out, this is not really
applicable, since this is a criterion tailored to what Skorstengaard
is aiming to do. We might consider what the equivalently tailored
criterion would be for us -- usable in "dynamic enforcement
environments" with potentially unsafe commodity compilers.

LEO: I'm REALLY not sure about this:
APT: Reviewer C interprets (4) to mean:
"This criterion asks for an argument that any property of a program
that relies on stack safety can be proven with the characterization of stack safety."
Since we're in the business of _defining_ stack safety, this seems pretty circular to me!
Maybe the point is that we should not omit any characteristic of
everyone's informal notion of stack safety (for the set of language features
we support -- which is the business of (5)).  Can we claim that (informally, of course)?
(4) complete: Subject to the limitations of the formalization, our
properties should apply to any reasonable program.

(5) scalable: Dynamic code would pose a significant challenge in this
setup. In the tag world, we could handle generated code by tagging the
instructions that generate it, which would correspond to a map that
allows some instructions to update the maps, including potentially
itself.  On the other hand, we described how we would handle
coroutines, and threads would be similar. Basically when we lose the
monotonicity of contours relative to stack depth, we will
need to change the LSE property to check integrity and confidentiality
each time we cross between security contexts - nested calls are not
strictly more limited.

@@

>   Do you really think so and if so, why do you think their approach could not be applied to a different enforcement mechanism?

APT:  Sk2019b _define_ stack safety via a capability machine semantics that is supposed to embody stack
safety "by construction," and relating it to a standard semantics for the same machine via a full abstraction result.
We did not mean to imply that the same idea could not work for other machine models or enforcement mechanisms (although
this generalization is not actually in Sk2019b, even as suggested future work). Rather, we wished to distinguish our
approach from theirs by emphasizing that we define stack safety based not on any "correct by construction"
machine tied to some flavor of enforcement,  but rather on more abstract notions of observable behavior.

BCP: Nice.

> * What exactly is the benefit of your approach to defining stack safety w.r.t. the approach of Skorstengaard 2019b?
>   Do you think it can be applied to more or less languages?
>   Do you think it is better suited or less well suited for reasoning about programs which depend on stack safety?
>   Do you think it is etc.
>
> * Do you think you could show safety of a specific example program that depends on stack safety (like the awkward example) and if so, how would such a proof work?
>
> * Do you think your approach to defining stack safety could be extended to languages with the following features (and if so, how?):
>   - varargs?  (seems problematic for call map)
>   - dynamic code generation (seems problematic for the function map, call map and return map)
>   - dynamic linking (seems problematic for the function map, call map and return map)
>   - self-editing code (seems problematic for call map and return map)
>   - tail calls (seems potentially okay, but I'd like to be sure)
>   - exceptions and stack unwinding
>   - closures (seems potentially problematic for precision of the entry map)
>   How would you extend your approach to define stack safety in the presence of these features?
>
> * Do you think your approach implies the following properties?
>   - temporal safety in the presence of closures (i.e. closures should only be invokable by the adversary after the adversary first receives a reference to them)
>   - encapsulation of closures: it should not be possible for the adversary to invoke a closure with a different environment than the one they received?
>   If not, do you think it should imply these properties and if so, how do you think it could be extended?

  Adding closures requires:
  - identifying code points where closures are created
  - adding machinery to track association of closure identities, entry points, and components
    containing valid closure pointers (including pointer provenance, as with stack-derived pointers)
  - extending WBCF to require that closure invocations respect the closure's designated entry point
    and use a valid closure pointer (ensuring temporal safety and encapsulation)
  - extending contours to treat some components as sealed, associated with closure identities
  - on closure invocation, set contour for encapsulated components to LC/LI, other components as normal for stack safety
    (allowing access to closure)
  - otherwise treat sealed components as HC/HI except that from a caller's perspective, they might change during
    nested calls (monotonicity is lost)

  The answers are yes, we believe that with addition of closures, natural extensions to WBCF and LSE would imply these
  properties.

> * Are the lazy and strong variant of your properties specifically intended for the corresponding micropolicy-based enforcement techniques or do you believe they are more broadly applicable?

### 2020-09-09 rebuttal.txt

BCP: Nice.

> * What exactly is the benefit of your approach to defining stack safety w.r.t. the approach of Skorstengaard 2019b?
>   Do you think it can be applied to more or less languages?
>   Do you think it is better suited or less well suited for reasoning about programs which depend on stack safety?
>   Do you think it is etc.
>
> * Do you think you could show safety of a specific example program that depends on stack safety (like the awkward example) and if so, how would such a proof work?
>
> * Do you think your approach to defining stack safety could be extended to languages with the following features (and if so, how?):
>   - varargs?  (seems problematic for call map)
>   - dynamic code generation (seems problematic for the function map, call map and return map)
>   - dynamic linking (seems problematic for the function map, call map and return map)
>   - self-editing code (seems problematic for call map and return map)
>   - tail calls (seems potentially okay, but I'd like to be sure)
>   - exceptions and stack unwinding
>   - closures (seems potentially problematic for precision of the entry map)
>   How would you extend your approach to define stack safety in the presence of these features?
>
> * Do you think your approach implies the following properties?
>   - temporal safety in the presence of closures (i.e. closures should only be invokable by the adversary after the adversary first receives a reference to them)
>   - encapsulation of closures: it should not be possible for the adversary to invoke a closure with a different environment than the one they received?
>   If not, do you think it should imply these properties and if so, how do you think it could be extended?

SNA:
  Adding closures requires:
  - identifying code points where closures are created
  - adding machinery to track association of closure identities, entry points, and components
    containing valid closure pointers (including pointer provenance, as with stack-derived pointers)
  - extending WBCF to require that closure invocations respect the closure's designated entry point
    and use a valid closure pointer (ensuring temporal safety and encapsulation)
  - extending contours to treat some components as sealed, associated with closure identities
  - on closure invocation, set contour for encapsulated components to LC/LI, other components as normal for stack safety
    (allowing access to closure)
  - otherwise treat sealed components as HC/HI except that from a caller's perspective, they might change during
    nested calls (monotonicity is lost)

### 2020-09-09 rebuttal.txt

ATTACKER MODEL

Finally, reviewer C is also concerned with the attacker model. The attacker
model we consider is discussed in Section 2.  In particular, lines 104-106
state that "the attacker can run arbitrary machine code" and that "hardware
and timing attacks are out of scope". The attacker model of the micropolicy
enforcement mechanism is described in [Roessler and Dehon 18].

BCP: Can we sketch it here?

> Review #27A
> ===========================================================================
>
> Overall merit
> -------------
> B. Weak Accept
>
> Reviewer expertise
> ------------------
> Y. Knowledgeable
>
> Paper summary
> -------------
> This paper defines an abstraction of stack safety in a positive way, meaning defining what operations are allowed. This work improves upon a previous work, which also defines stack safety in a positive way, but whose definitions are tied to capability machines. this work generalizes the stack safety definitions to be applicable to a wide class of  enforcement mechanisms.
>
> Strengths
> ---------
> + The authors addresses an important problem in software security with a solid methodology. Indeed, stack safety defined in a negative way leads to arm races between defenses and attacks.
>
>  + The definitions and theory in this work seem sound
>
>  + The authors apply the proposed the stack safety definitions to characterize two variations of enforcement policies that uses tag-based hardware. The characterization enables us to precisely understand what is the safety achieved by the enforcement policy and what safety is lost to achieve a faster implementation.
>
> Weaknesses
> ----------
> - The authors do not explicitly discuss how multiple concurrent threads fit in the definition. It is not clear to me how to apply the definitions in this work to multiple threads. Since the stacks of all threads are allocated in the same linear virtual address space, it is possible for one thread’s stack to overlap the stack of another thread. How should stack safety be defined in this case? I think this is an very important question as recent work points out cross-thread stack smashing attack [1].

We sketch how multiple threads/coroutines would work in the future
work section (l 1213-1219). In particular, we would need to further
distinguish stack locations as either "accessible" (current frame),
"belonging to the same call stack", or "belonging in another
stack". And then integrity would require that when a function changes
the locations in the "same" stack should be unchanged. Similarly for
cofnidentiality.

@@

>  - In the future work section, the authors mentions several types of non-stack control flow that are not addressed by the current model, including tail calls. Other common non-stack control flow includes exceptions (such as c++ exceptions) and setjmp/longjmp. I understand that these non-stack control flow is more difficult to model, but for the exact reasons, how to formally characterize stack safety for these difficult cases becomes critical.

LEO: Not sure what the take should be here. Something like the following?
Tail calls were left out as it's only the characterization of the return that poses
a problem - once the point of context switch is determined, the statement of
stack safety remains largely the same.

>  [1] Xiaoyang Xu, Masoud Ghaffarinia, Wenhao Wang, Kevin W. Hamlen, and Zhiqiang Lin. 2019. CONFIRM: evaluating compatibility and relevance of control-flow integrity protections for modern software. In Proceedings of the 28th USENIX Conference on Security Symposium (SEC’19). USENIX Association, USA, 18051821.
>
> Comments for author
> -------------------
> Please see the weaknesses section.
>
>
>
> Review #27B
> ===========================================================================
>
> Overall merit
> -------------
> D. Strong Reject
>
> Reviewer expertise
> ------------------
> Y. Knowledgeable
>
> Paper summary
> -------------
> This paper:
> - Defines stack safety as confidentiality, integrity, and well-bracketedness.
> - Evaluates existing stack protection mechanisms w.r.t. the defined notion of stack safety.
> - Proposes other protection mechanisms.
>
> Strengths
> ---------
> - This paper is clearly defining a notion of stack safety.
>
> Weaknesses
> ----------
> - The proposed notion of stack safety is too strong to be used for real-world programs.
> - The proposed notion of stack safety is too strong to be enforced by existing stack protection mechanisms.
> - This paper is lacking proper discussion on related work.
>
> Comments for author
> -------------------
> This paper is not clearly motivated, and as a result, has the following problems:
>
> - The proposed notion of stack safety is too strong to be used for real-world programs.
>
>   As discussed in Section 9, stack-derived pointers are not supported (L1199), but they are widely used in real-world programs.
>   Furthermore, without stack-derived pointers, stack safety is more-or-less obvious to define.

Leo: The sketch of stack-derived pointers in 1199 seems fairly intuitive to me. Double down on it?

> - The proposed notion of stack safety is too strong to be enforced by existing stack protection mechanisms.
>
>   [Roessler and DeHon 2018]'s "lazy tagging and clearing" is itself not stack-safe according to this paper.
>   To understand the mechanism, this paper additionally defines the "observable" versions of stack safety.
>   But then why you didn't use the observable version as the authoritative definition?

@@

> ---------------------------------
> * You seem to say/suggest that the approach of Skorstengaard 2019b to defining stack safety is specific to capability machines.
>   Do you really think so and if so, why do you think their approach could not be applied to a different enforcement mechanism?

Sk2019b _define_ stack safety via a capability machine semantics that is supposed to embody stack
safety "by construction," and relating it to a standard semantics for the same machine via a full abstraction result.
We did not mean to imply that the same idea could not work for other machine models or enforcement mechanisms (although
this generalization is not actually in Sk2019b, even as suggested future work). Rather, we wished to distinguish our
approach from theirs by emphasizing that we define stack safety based not on any "correct by construction"
machine tied to some flavor of enforcement,  but rather on more abstract notions of observable behavior.
